Hippocampal replay of experience at slow speeds

### 2021-04-28 Article.tex
Update on Overleaf.

One possibility is that these events are supported by different subcircuits within the hippocampus. For example, \cite{OlivaOriginGammaFrequency2018a} showed that layer 2/3 neurons in the entorhinal cortex increased their firing 50 ms before the start of longer duration SWRs (>100 ms), but not before the start of shorter duration SWRs, suggesting that

>>>>

One possibility is that these events are supported by different subcircuits within the hippocampus.  For example, \cite{YamamotoDirectMedialEntorhinal2017} found that blocking medial entorhinal cortex (MEC) output to CA1 resulted in shorter replay trajectories and \cite{OlivaOriginGammaFrequency2018} showed that layer 2/3 MEC neurons increased their firing 50 ms before the start of longer duration SWRs (>100 ms). This raises the possibility that these slower replays are driven by CA3-CA1 interaction while the faster trajectories are more externally driven by MEC-CA1. Our
